### 2013-12-11 mcmc.tex
paragraph about initialization

...Precede with optimization
% BJB
% If applicable. Bad idea in high dimension/underconstrained
% problem.

>>>>

Just as most (though not all) MCMC methods require a choice of proposal distribution,
  most (though not all) require a choice about initialization:
The walker needs (or walkers need) to be started somewhere in the parameter space.
In many use cases for MCMC,
  the investigator wants to use it to obtain uncertainty information about
  or propagate uncertainty into parameter estimates.
In these cases, it makes sense to initialize the walker or walkers at sensible parameter estimates,
  found by optimizing a likelihood or a posterior PDF in advance of sampling.
In extremely high dimensions (large numbers of parameters), this can be a bad idea,
  since the optimal parameters are not necessarily near typical posterior samples,
  but in low dimensions (few to tens) this is often sensible.

In other use cases,
  the investigator wants to use MCMC to search all of parameter space
  for good models, and also sample.
In this case, it makes sense to be more catholic with initialization...

...but note that MCMC is not the ideal search algorithm for any parameter space.
